Impact of Education on Entrepreneurship - Data Gathering and Analysis

### 2014-11-28 GEMDataSource.Rmd
Created subset of new GEM data

# Recode countries
Merged9$Country[Merged9$Country == "AUSTRALIA"] <- "Australia"
Merged9$Country[Merged9$Country == "AUSTRIA"] <- "Austria"
Merged9$Country[Merged9$Country == "BELGIUM"] <- "Belgium"
Merged9$Country[Merged9$Country == "CANADA"] <- "Canada"
Merged9$Country[Merged9$Country == "CHILE"] <- "Chile"
Merged9$Country[Merged9$Country == "CZECH REPUBLIC"] <- "Czech Republic"
Merged9$Country[Merged9$Country == "DENMARK"] <- "Denmark"
Merged9$Country[Merged9$Country == "ESTONIA"] <- "Estonia"
Merged9$Country[Merged9$Country == "FINLAND"] <- "Finland"
Merged9$Country[Merged9$Country == "FRANCE"] <- "France"
Merged9$Country[Merged9$Country == "GERMANY"] <- "Germany"
Merged9$Country[Merged9$Country == "GREECE"] <- "Greece"
Merged9$Country[Merged9$Country == "HUNGARY"] <- "Hungary"
Merged9$Country[Merged9$Country == "ICELAND"] <- "Iceland"
Merged9$Country[Merged9$Country == "IRELAND"] <- "Ireland"
Merged9$Country[Merged9$Country == "ISRAEL"] <- "Israel"
Merged9$Country[Merged9$Country == "ITALY"] <- "Italy"
Merged9$Country[Merged9$Country == "JAPAN"] <- "Japan"
Merged9$Country[Merged9$Country == "KOREA"] <- "South Korea"
Merged9$Country[Merged9$Country == "LUXEMBURG"] <- "Luxemburg"
Merged9$Country[Merged9$Country == "MEXICO"] <- "Mexico"
Merged9$Country[Merged9$Country == "NETHERLANDS"] <- "Netherlands"
Merged9$Country[Merged9$Country == "NEW ZEALAND"] <- "New Zealand"
Merged9$Country[Merged9$Country == "NORWAY"] <- "Norway"
Merged9$Country[Merged9$Country == "POLAND"] <- "Poland"
Merged9$Country[Merged9$Country == "PORTUGAL"] <- "Portugal"
Merged9$Country[Merged9$Country == "SLOVAK REPUBLIC"] <- "Slovak Republic"
Merged9$Country[Merged9$Country == "SLOVENIA"] <- "SLOVENIA"
Merged9$Country[Merged9$Country == "SPAIN"] <- "Spain"
Merged9$Country[Merged9$Country == "SWEDEN"] <- "Sweden"
Merged9$Country[Merged9$Country == "SWITZERLAND"] <- "Switzerland"
Merged9$Country[Merged9$Country == "TURKEY"] <- "Turkey"
Merged9$Country[Merged9$Country == "UNITED KINGDOM"] <- "United Kingdom"
Merged9$Country[Merged9$Country == "UK"] <- "United Kingdom"
Merged9$Country[Merged9$Country == "USA"] <- "United States"
Merged9$Country[Merged9$Country == "UNITED STATES"] <- "United States"

LongGEM<- melt(data = Merged9,
                  id.vars = c("Country"),
                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010"))

@@

################### Difficult Section #####################

# Grab the rows we need
myvars <- c("Australia", "Austria", "Belgium", "Canada", "Chile", "Czech Republic", "Denmark", "Estonia", "Finland", "France", "Germany", "Greece", "Hungary", "Iceland", "Ireland", "Israel", "Italy", "Japan", "Korea", "Luxemburg", "Mexico", "Netherlands", "New Zealand", "Norway", "Poland", "Portugal", "Slovak Republic", "Slovenia", "Spain", "Sweden", "Switzerland", "Turkey", "United Kingdom", "United States")

Long2[,"Support"] <- as.numeric(Long2[,"Support"])
Long2[,"Year"] <- as.numeric(Long2[,"Year"])
Long2[,"Country"] <- as.factor(Long2[,"Country"])

Long2

Long2[c("Australia", "Austria", "Belgium", "Canada", "Chile", "Czech Republic", "Denmark", "Estonia", "Finland", "France", "Germany", "Greece", "Hungary", "Iceland", "Ireland", "Israel", "Italy", "Japan", "Korea", "Luxemburg", "Mexico", "Netherlands", "New Zealand", "Norway", "Poland", "Portugal", "Slovak Republic", "Slovenia", "Spain", "Sweden", "Switzerland", "Turkey", "United Kingdom", "United States"), ]

# Grab only countries we need
NewData <- Long2[rownames = myvars, 
                 colnames = mystats]

mystats <- c("Country", "Year", "Support")

NewData1 <- data.frame(NewData)

>>>>

# Recode countries
Merged9$Country[Merged9$Country == "AUSTRALIA"] <- "Australia"
Merged9$Country[Merged9$Country == "AUSTRIA"] <- "Austria"
Merged9$Country[Merged9$Country == "BELGIUM"] <- "Belgium"
Merged9$Country[Merged9$Country == "CANADA"] <- "Canada"
Merged9$Country[Merged9$Country == "CHILE"] <- "Chile"
Merged9$Country[Merged9$Country == "CZECH REPUBLIC"] <- "Czech Republic"
Merged9$Country[Merged9$Country == "DENMARK"] <- "Denmark"
Merged9$Country[Merged9$Country == "ESTONIA"] <- "Estonia"
Merged9$Country[Merged9$Country == "FINLAND"] <- "Finland"
Merged9$Country[Merged9$Country == "FRANCE"] <- "France"
Merged9$Country[Merged9$Country == "GERMANY"] <- "Germany"
Merged9$Country[Merged9$Country == "GREECE"] <- "Greece"
Merged9$Country[Merged9$Country == "HUNGARY"] <- "Hungary"
Merged9$Country[Merged9$Country == "ICELAND"] <- "Iceland"
Merged9$Country[Merged9$Country == "IRELAND"] <- "Ireland"
Merged9$Country[Merged9$Country == "ISRAEL"] <- "Israel"
Merged9$Country[Merged9$Country == "ITALY"] <- "Italy"
Merged9$Country[Merged9$Country == "JAPAN"] <- "Japan"
Merged9$Country[Merged9$Country == "KOREA"] <- "South Korea"
Merged9$Country[Merged9$Country == "LUXEMBURG"] <- "Luxemburg"
Merged9$Country[Merged9$Country == "MEXICO"] <- "Mexico"
Merged9$Country[Merged9$Country == "NETHERLANDS"] <- "Netherlands"
Merged9$Country[Merged9$Country == "NEW ZEALAND"] <- "New Zealand"
Merged9$Country[Merged9$Country == "NORWAY"] <- "Norway"
Merged9$Country[Merged9$Country == "POLAND"] <- "Poland"
Merged9$Country[Merged9$Country == "PORTUGAL"] <- "Portugal"
Merged9$Country[Merged9$Country == "SLOVAK REPUBLIC"] <- "Slovak Republic"
Merged9$Country[Merged9$Country == "SLOVENIA"] <- "SLOVENIA"
Merged9$Country[Merged9$Country == "SPAIN"] <- "Spain"
Merged9$Country[Merged9$Country == "SWEDEN"] <- "Sweden"
Merged9$Country[Merged9$Country == "SWITZERLAND"] <- "Switzerland"
Merged9$Country[Merged9$Country == "TURKEY"] <- "Turkey"
Merged9$Country[Merged9$Country == "UNITED KINGDOM"] <- "United Kingdom"
Merged9$Country[Merged9$Country == "UK"] <- "United Kingdom"
Merged9$Country[Merged9$Country == "USA"] <- "United States"
Merged9$Country[Merged9$Country == "UNITED STATES"] <- "United States"
Merged9$Country[Merged9$Country == "Korea"] <- "South Korea"

# Change merged data from wide to long
LongGEM<- melt(data = Merged9,
                  id.vars = c("Country"),
                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010"))

@@

# Create a vector with OECD countries
myvars <- c('Australia', 'Austria', 'Belgium', 'Canada', 'Chile', 'Czech Republic', 'Denmark', 'Estonia', 'Finland', 'France', 'Germany', 'Greece', 'Hungary', 'Iceland', 'Ireland', 'Israel', 'Italy', 'Japan', 'Korea', 'Luxemburg', 'Mexico', 'Netherlands', 'New Zealand', 'Norway', 'Poland', 'Portugal', 'Slovak Republic', 'Slovenia', 'Spain', 'Sweden', 'Switzerland', 'Turkey', 'United Kingdom', 'United States')

# Subset LongGEM with the countries we need
subset_data <- subset(LongGEM, Country %in% myvars)

# Delete unnecessary column
subset_data$row.name <- NULL

# Arrange subset_data by country and year
GrandData <- arrange(subset_data, Country, Year)

########### STUCK #############

FinalData <- merge(CompleteDataset, subset_data,
                   union("Country", "Year"),
                   all = TRUE)
